---
title: "cantoneseMost"
output: html_document
---
## Setup 

```{r setup}
source("BAhelperFunctions.R")
library(ggplot2)
library(plyr)
library(gridExtra)

load("dataset.RData")

alldata_adjMost$correct <- with(alldata_adjMost, ifelse(corrAns == TRUE, key_resp_TrueFalse.keys == "f", key_resp_TrueFalse.keys == "j"))
head(alldata_adjMost[c("corrAns","key_resp_TrueFalse.keys","correct")])
alldata_propMost$correct <- with(alldata_propMost, ifelse(corrAns == TRUE, key_resp_TrueFalse.keys == "f", key_resp_TrueFalse.keys == "j"))
```


First, get rid of every trial where the response wasn't 1 or 0
```{r}
alldata_propMost$correct <- as.numeric(alldata_propMost$correct)
alldata_adjMost$correct <- as.numeric(alldata_adjMost$correct)

#combine prop/det most and adj/largest-subset most dfs 
allData <- rbind(alldata_propMost, alldata_adjMost)
```


```{r}
ddply(allData, .(participant), summarize, meanAcc=mean(correct))
```

Remove any participants 
```{r}
allData -> backupCantoneseMost
allData <- subset(backupCantoneseMost, participant!=14) #can't be fit -- below 60% overall 
```

##Det most v. Adj most
Get overall participant avgs by ratio
```{r}
#how many participants do we have? 
length(levels(as.factor(allData$participant))) -> numParticipants

#for each subject 
bySubj <- ddply(allData, .(question, participant, ratioBin), summarize, meanAcc=mean(correct))

#for the group
groupAvgs <- ddply(bySubj, .(question, ratioBin), summarize, meanCorrect=mean(meanAcc), se=sd(meanAcc)/sqrt(numParticipants))
groupAvgs$upper <- groupAvgs$meanCorrect + groupAvgs$se
groupAvgs$lower <- groupAvgs$meanCorrect - groupAvgs$se
```


Fit w and g for each of these two groups, then get predicted values for each ratio
```{r}
#fit to binned data 
fits <- ddply(groupAvgs, .(question), summarize, 
              w=mle.weber.guess(r=ratioBin, meanCorrect)[[1]][1], g=mle.weber.guess(r=ratioBin, meanCorrect)[[1]][2])

#fit to raw data 
fitsRaw <- ddply(allData, .(question), summarize, 
              w=mle.weber.guess(r=ratio, correct)[[1]][1], g=mle.weber.guess(r=ratio, correct)[[1]][2])

modelFits.group <- data.frame(y.values=NA, r.values=NA, quantifier=NA)
r.values <- seq(1,2,by=.001)

for (i in 1:nrow(fits)){
  paramList <- c(fits[i,]$w, fits[i,]$g)
  y <- weber.model.guess(params=paramList, r=r.values)
  currentQuant <- fits[i,]$question
  temp <- data.frame(y.values=y, r.values=r.values, quantifier=currentQuant)
  modelFits.group <- rbind(modelFits.group, temp)
}
modelFits.group <- modelFits.group[-1,] #get rid of the first row 

fits
```

Plot overall group accuracy 
```{r}
ggplot(data=groupAvgs) + geom_point(aes(x=ratioBin, y=meanCorrect, color=question)) + theme_bw() + 
  scale_y_continuous(limits = c(.5,1)) + ggtitle("Overall Group Data") + 
  geom_errorbar(aes(x=ratioBin, ymax=upper, ymin=lower, color=question), size=0.15, width=.05) +
  theme_bw() + theme(text = element_text(size=20)) + geom_line(data=modelFits.group, aes(x=r.values,y=y.values,color=quantifier))
```

##Now look at how this changes given # of distractor sets 
Get overall participant avgs by bins 
```{r}
#for each subject 
bySubj_byDistractors <- ddply(allData, .(question, participant, numberDistractorSets, ratioBin), summarize, meanAcc=mean(correct))

#for the group
groupAvgs_byDistractors <- ddply(bySubj_byDistractors, .(question, numberDistractorSets, ratioBin), summarize, meanCorrect=mean(meanAcc), 
                                 se=sd(meanAcc)/sqrt(numParticipants))
groupAvgs_byDistractors$upper <- groupAvgs_byDistractors$meanCorrect + groupAvgs_byDistractors$se
groupAvgs_byDistractors$lower <- groupAvgs_byDistractors$meanCorrect - groupAvgs_byDistractors$se
```

Fit w and g for each of these two groups, then get predicted values for each ratio
```{r}
#fit to binned data
fits_byDistractors <- ddply(groupAvgs_byDistractors, .(question, numberDistractorSets), summarize, 
                            w=mle.weber.guess(r=ratioBin, meanCorrect)[[1]][1], g=mle.weber.guess(r=ratioBin, meanCorrect)[[1]][2])

#fit to raw data 
fitsRaw_byDistractors <- ddply(allData, .(question, numberDistractorSets), summarize, 
              w=mle.weber.guess(r=ratio, correct)[[1]][1], g=mle.weber.guess(r=ratio, correct)[[1]][2])

modelFits.distractor <- data.frame(y.values=NA, r.values=NA, quantifier=NA, numberDistractorSets=NA)
r.values <- seq(1,2,by=.001)

for (i in 1:nrow(fits_byDistractors)){
  paramList <- c(fits_byDistractors[i,]$w, fits_byDistractors[i,]$g)
  y <- weber.model.guess(params=paramList, r=r.values)
  currentQuant <- fits_byDistractors[i,]$question
  numDistractors <- fits_byDistractors[i,]$numberDistractorSets
  temp <- data.frame(y.values=y, r.values=r.values, quantifier=currentQuant, numberDistractorSets=numDistractors)
  modelFits.distractor <- rbind(modelFits.distractor, temp)
}
modelFits.distractor <- modelFits.distractor[-1,] #get rid of the first row 

fits_byDistractors
```

Plot the overall group accuracy by number of distractor sets 
```{r}
ggplot(data=groupAvgs_byDistractors) + geom_point(aes(x=ratioBin, y=meanCorrect, color=question)) + 
  scale_y_continuous(limits = c(.48,1), breaks=c(.5,.75,1)) + ggtitle("Overall Group Data, by # distractor sets") + facet_wrap(~numberDistractorSets) +
  geom_errorbar(aes(x=ratioBin, ymax=upper, ymin=lower, color=question), size=0.15, width=.05) +
  theme_bw() + theme(text = element_text(size=20)) + geom_line(data=modelFits.distractor, aes(x=r.values,y=y.values,color=quantifier)) +
  ylab("mean correct") + xlab("ratio")

ggsave(filename = "cantoneseMost.png", width = 26.458333333, height = 17.859375, units = "cm")
```

##Stats
5 (ratio bins) x 4 (number distractor sets) x 2 (quantifier) anova 
5 (ratio bins) x 4 (number distractor sets) anova for each quantifier 
```{r}
forAnova <- bySubj_byDistractors 
forAnova$distractors <- as.factor(forAnova$numberDistractorSets)
forAnova$ratios <- as.factor(forAnova$ratioBin)
forAnova$participants <- as.factor(forAnova$participant)

#aov(meanAcc ~ ratioBin * distractors * question + Error(participant/(ratioBin * distractors * question)),
#    data=forAnova) -> fullAnova
#summary(fullAnova) 

print("--------------------------------prop most---------------------------------------------------")

aov(meanAcc ~ ratios * distractors + Error(participants/(ratios * distractors)), 
    data=subset(forAnova, question=="propMost")) -> propMostAnova
summary(propMostAnova)

print("--------------------------------adj most---------------------------------------------------")

aov(meanAcc ~ ratios * distractors + Error(participants/(ratios * distractors)), 
    data=subset(forAnova, question=="adjMost")) -> adjMostAnova
summary(adjMostAnova)
```

##Separate further by whether the correct answer was TRUE or FALSE 
Get overall participant avgs by bins 
```{r}
#for each subject 
bySubj_byTF <- ddply(allData, .(question, participant, corrAns, numberDistractorSets, ratioBin), summarize, meanAcc=mean(correct))

#for the group
groupAvgs_byTF <- ddply(bySubj_byTF, .(question, corrAns, numberDistractorSets, ratioBin), summarize, meanCorrect=mean(meanAcc), 
                                 se=sd(meanAcc)/sqrt(numParticipants))
groupAvgs_byTF$upper <- groupAvgs_byTF$meanCorrect + groupAvgs_byTF$se
groupAvgs_byTF$lower <- groupAvgs_byTF$meanCorrect - groupAvgs_byTF$se
```

Fit w and g for each of these two groups, then get predicted values for each ratio
```{r}
#fit to binned data
fits_byTF <- ddply(groupAvgs_byTF, .(question, corrAns, numberDistractorSets), summarize, 
                            w=mle.weber.guess(r=ratioBin, meanCorrect)[[1]][1], g=mle.weber.guess(r=ratioBin, meanCorrect)[[1]][2])

#fit to raw data 
fitsRaw_byTF <- ddply(allData, .(question, corrAns, numberDistractorSets), summarize, 
              w=mle.weber.guess(r=ratio, correct)[[1]][1], g=mle.weber.guess(r=ratio, correct)[[1]][2])

modelFits.TF <- data.frame(y.values=NA, r.values=NA, quantifier=NA, corrAns=NA, numberDistractorSets=NA)
r.values <- seq(1,2,by=.001)

for (i in 1:nrow(fits_byTF)){
  paramList <- c(fits_byTF[i,]$w, fits_byTF[i,]$g)
  y <- weber.model.guess(params=paramList, r=r.values)
  currentQuant <- fits_byTF[i,]$question
  corrAns <- fits_byTF[i,]$corrAns
  numberDistractors <- fits_byTF[i,]$numberDistractorSets
  temp <- data.frame(y.values=y, r.values=r.values, quantifier=currentQuant, corrAns=corrAns, numberDistractorSets=numberDistractors)
  modelFits.TF <- rbind(modelFits.TF, temp)
}
modelFits.TF <- modelFits.TF[-1,] #get rid of the first row 

fits_byTF
```

Plot the overall group accuracy by number of distractor sets and correct answer. One thing to notice is that with the 3 and 4 distractor trials, people seem to be answering FALSE for the adjMost question. It's just too hard and they're kind of giving up. But if we look at the screens where both stims are identical -- the 1 distractor cases -- we see the same patterns Tomasziewicz 2011 found in Polish. propMost is basically unaffected, but adjMost shows the "yes" bias (tendency to overestimate the target set). In the true cases, adjMost is better than propMost, which is what we'd expect. In any case, it shows the algorithms are distinct even when the displays are identical. 
```{r}
ggplot(data=groupAvgs_byTF) + geom_point(aes(x=ratioBin, y=meanCorrect, color=question)) + 
  scale_y_continuous(limits = c(.2,1), breaks=c(.25, .5,.75,1)) + ggtitle("Overall Group Data, by correct answer") + 
  geom_errorbar(aes(x=ratioBin, ymax=upper, ymin=lower, color=question), size=0.15, width=.05) + 
  geom_line(data=modelFits.TF, aes(x=r.values,y=y.values,color=quantifier)) + 
  facet_grid(numberDistractorSets~corrAns) + theme_bw() + theme(text = element_text(size=20)) 

ggsave(filename = "cantoneseMost_byTF.png", width = 26.458333333, height = 17.859375, units = "cm")
```

Zoom in on those identical display cases 
```{r}
identicalDisplays.avg <- subset(groupAvgs_byTF, numberDistractorSets==1)
identicalDisplays.fits <- subset(modelFits.TF, numberDistractorSets==1)

ggplot(data=identicalDisplays.avg) + geom_point(aes(x=ratioBin, y=meanCorrect, color=question)) + 
  scale_y_continuous(limits = c(.35,1), breaks=c(.5,.75,1)) + ggtitle("1-distractor displays, by correct answer") + 
  geom_errorbar(aes(x=ratioBin, ymax=upper, ymin=lower, color=question), size=0.15, width=.05) + 
  geom_line(data=identicalDisplays.fits, aes(x=r.values,y=y.values,color=quantifier)) + 
  facet_wrap(~corrAns) + theme_bw() + theme(text = element_text(size=20)) + ylab("mean correct") + xlab("ratio")

ggsave(filename = "cantoneseMost_identicalDisplays.png", width = 26, height = 14, units = "cm")
```

And run stats on the identical screens -- main effect of ratio, marginal main effect of correct answer, significant interaction b/t quantifier and correct answer 
```{r}
forAnova.identicalDisplays <- subset(bySubj_byTF, numberDistractorSets==1)
forAnova.identicalDisplays$answer <- as.factor(forAnova.identicalDisplays$corrAns)
forAnova.identicalDisplays$ratios <- as.factor(forAnova.identicalDisplays$ratioBin)
forAnova.identicalDisplays$participants <- as.factor(forAnova.identicalDisplays$participant)

aov(meanAcc ~ question*ratios*answer + Error(participants/(question*ratios*answer)), 
    data=forAnova.identicalDisplays) -> identicalAnova
summary(identicalAnova)
```



##Individual fits 
Input raw ratios (not binned) and accuracy on a given trial for each participant
```{r}
#fit to binned data
fits_bySubj <- ddply(bySubj_byDistractors, .(participant, question, numberDistractorSets), summarize, 
                            w=mle.weber.guess(r=ratioBin, meanAcc)[[1]][1], g=mle.weber.guess(r=ratioBin, meanAcc)[[1]][2])

#fit to raw data 
fitsRaw_bySubj <- ddply(allData, .(participant, question, numberDistractorSets), summarize, 
              w=mle.weber.guess(r=ratio, correct)[[1]][1], g=mle.weber.guess(r=ratio, correct)[[1]][2])

modelFits.subj <- data.frame(y.values=NA, r.values=NA, participant=NA, quantifier=NA, numberDistractorSets=NA)
r.values <- seq(1,2,by=.001)

for (i in 1:nrow(fitsRaw_bySubj)){
  paramList <- c(fitsRaw_bySubj[i,]$w, fitsRaw_bySubj[i,]$g)
  participant <- fitsRaw_bySubj[i,]$participant
  y <- weber.model.guess(params=paramList, r=r.values)
  currentQuant <- fitsRaw_bySubj[i,]$question
  numDistractors <- fitsRaw_bySubj[i,]$numberDistractorSets
  temp <- data.frame(y.values=y, r.values=r.values, participant=participant, quantifier=currentQuant, numberDistractorSets=numDistractors)
  modelFits.subj <- rbind(modelFits.subj, temp)
}
modelFits.distractor <- modelFits.distractor[-1,] #get rid of the first row 
modelFits.subj <- modelFits.subj[-1,] #get rid of the first row 

fitsRaw_bySubj
```

Plot the individual fits 
```{r}
ggplot(data=bySubj_byDistractors) + geom_point(aes(x=ratioBin, y=meanAcc, color=question)) + 
  scale_y_continuous(limits = c(.48,1), breaks=c(.5,.75,1)) + ggtitle("Individual data, by # distractor sets") +
  #geom_errorbar(aes(x=ratioBin, ymax=upper, ymin=lower, color=question), size=0.15, width=.05) +
  geom_line(data=modelFits.subj, aes(x=r.values,y=y.values,color=quantifier)) + 
  facet_grid(participant~numberDistractorSets) + 
  theme_bw() + theme(text = element_text(size=20))

ggsave(filename = "cantoneseMost_bySubjs.png", width = 30, height = 35, units = "cm")
```

##Violin plots

```{r}
avgW <- ddply(fitsRaw_bySubj, .(question, numberDistractorSets), summarize, meanW=mean(w),
              se=sd(w)/sqrt(length(unique(fitsRaw_bySubj$participant)))) 

ggplot(data=fitsRaw_bySubj) + geom_violin(aes(x=as.factor(numberDistractorSets),y=w,fill=as.factor(numberDistractorSets))) + 
  geom_point(aes(x=as.factor(numberDistractorSets),y=w), size=1) + 
  geom_point(data=avgW, aes(x=as.factor(numberDistractorSets), y=meanW), size=10, shape="--", color="yellow") + 
  facet_wrap(~question) + theme_bw() 
```

